### 2024-08-02 getting-started.qmd
20240801 - garbage collection

@@

@@

@@

@@

>>>>

# garbage collection
rm(nfl_pbp_raw)
gc()
```

@@

# garbage collection
rm(nfl_4thdown_raw)
rm(nfl_4thdown)
gc()
```

@@

# garbage collection
rm(nfl_participation_raw)
rm(nfl_participation)
gc()
```

@@

# garbage collection
rm(nfl_expectedFantasyPoints_weekly_raw)
rm(nfl_expectedFantasyPoints_pbp_raw)
rm(nfl_expectedFantasyPoints_weekly)
rm(nfl_expectedFantasyPoints_pbp)
gc()
```

@@

# garbage collection
rm(nfl_pbp)
gc()
```
